---
title: | 
  | Assignment 4: Collaborating Together
  | Introduction to Applied Data Science
  | 2022-2023
author: |
  | Amelie van Dinther
  | A.e.vandinther@student.uu.nl
  | http://www.github.com/AmelievanDinther
date: April 2023
urlcolor: purplemro
linkcolor: purple
output: 
  pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error=TRUE)
```

## Assignment 4: Collaborating Together 

### Part 1: Contributing to another student's Github repository

In this assignment, you will create a Github repository, containing this document and the .pdf output, which analyzes a dataset individually using some of the tools we have developed. 

This time, make sure to not only put your name and student e-mail in your Rmarkdown header, but also your Github account, as I have done myself. 

However, you will also pair up with a class mate and contribute to each others' Github repository. Each student is supposed to contribute to another student's work by writing a short interpretation of 1 or 2 sentences at the designated place (this place is marked with **designated place**) in the other student's assignment. 

This interpretation will not be graded, but a Github shows the contributors to a certain repository. This way, we can see whether you have contributed to a repository of a class mate. 


**Question 1.1**: Fill in the __github username__ of the class mate to whose repository you have contributed. 

usethis::use_git_config(user.name = "AmelievanDinther",
               user.email = "A.e.vandinther@student.uu.nl")

[mselimunal]

### Part 2: Analyzing various linear models

In this part, we will summarize a dataset and create a couple of customized tables. Then, we will compare a couple of linear models to each other, and see which linear model fits the data the best, and yields the most interesting results.

We will use a dataset called `GrowthSW` from the `AER` package. This is a dataset containing 65 observations on 6 variables and investigates the determinants of economic growth. First, we will try to summarize the data using the `modelsummary` package. 

```{r, warning=FALSE, message=FALSE}
library(AER)
data(GrowthSW)
```

One of the variables in the dataset is `revolutions`, the number of revolutions, insurrections and coup d'etats in country $i$ from 1965 to 1995.

**Question 2.1**: Using the function `datasummary`, summarize the mean, median, sd, min, and max of the variables `growth`, and `rgdp60` between two groups: countries with `revolutions` equal to 0, and countries with more than 0 revolutions. Call this variable `treat`. Make sure to also write the resulting data set to memory. Hint: you can check some examples [here](https://vincentarelbundock.github.io/modelsummary/articles/datasummary.html#datasummary).

```{r}
library(modelsummary); library(tidyverse)

# write your code here

treat <- GrowthSW |>
  mutate(treat = if_else(revolutions > 0, "More than 0 Revolutions", "0 Revolutions"))

treat|>
  datasummary(formula = growth + rgdp60 ~ treat * (mean + median + sd + min + max))
```

**Designated place**: type one or two sentences describing this table of a fellow student below. For example, comment on the mean and median growth of both groups. Then stage, commit and push it to their github repository. 


### Part 3: Make a table summarizing reressions using modelsummary and kable

In question 2, we have seen that growth rates differ markedly between countries that experienced at least one revolution/episode of political stability and countries that did not. 

**Question 3.1**: Try to make this more precise this by performing a t-test on the variable growth according to the group variable you have created in the previous question. 

```{r}
# write t test here
GrowthSW$treat <- ifelse(GrowthSW$revolutions > 0, "More than 0 Revolutions", "0 Revolutions")

t.test(growth ~ treat, data = GrowthSW)


```

**Question 3.2**: What is the $p$-value of the test, and what does that mean? Write down your answer below.
The p-value = 0.06871 

if the P-value is less than the predetermined significance level (0.05 or 0.01) it is suggeststed that there is sufficient evidance to reject the 0 hypothesis. This would be an indication that there is a different in the mean growth rates between the 2 groups. the countries with and without revolution

is the P-value is greater than the significance level IN THIS CASE as it is 0.06871, there is not enough evidance to reject the 0 hypothesis. So the observes difference in mean growth rates between countries with and without revolution would be due to chance this does not provide strong evidance of a significant difference. 


We can also control for other factors by including them in a linear model, for example:

$$
\text{growth}_i = \beta_0 + \beta_1 \cdot \text{treat}_i + \beta_2 \cdot \text{rgdp60}_i + \beta_3 \cdot \text{tradeshare}_i + \beta_4 \cdot \text{education}_i + \epsilon_i
$$

**Question 3.3**: What do you think the purpose of including the variable `rgdp60` is? Look at `?GrowthSW` to find out what the variables mean. 

?GrowthSW  provides information about the dataset and its variables. 
We see than the rgdp60 variable shows the "value of GDP per capita in 1960, converted to 1960 US dollars". That is the purpose of including the rgdp60 variable. It helps to examine the realtionship between the initial GDP level and the subsequent economic growth rates in the dataset, providing insights into the determinants of economic growth. 

We now want to estimate a stepwise model. Stepwise means that we first estimate a univariate regression $\text{growth}_i = \beta_0 + \beta_1 \cdot \text{treat}_i + \epsilon_i$, and in each subsequent model, we add one control variable. 

**Question 3.4**: Write four models, titled `model1`, `model2`, `model3`, `model4` (using the `lm` function) to memory. Hint: you can also use the `update` function to add variables to an already existing specification.

```{r}
model1 <- lm(growth ~ treat, data = GrowthSW)
model2 <- update(model1, . ~ . + rgdp60)
model3 <- update(model2, . ~ . + education)
model4 <- update(model3, . ~ . + tradeshare)
save(model1, model2, model3, model4, file = "stepwise_models.RData")
```

Now, we put the models in a list, and see what `modelsummary` gives us:

```{r}
 list(model1, model2, model3, model4) |>
  modelsummary(stars=T, gof_map = c("nobs", "r.squared")
# edit this to remove the statistics other than R-squared
# and N
)

```

**Question 3.5**: Edit the code chunk above to remove many statistics from the table, but keep only the number of observations $N$, and the $R^2$ statistic. 

**Question 3.6**: According to this analysis, what is the main driver of economic growth? Why?
Focus on the coefficients associated with the variables. If a variable has  a p-value less than 0.05, it suggests that the variable is a potential driver of economic growth. So trade share is the main driveer of economic growth as this has a amount with one star and 

**Question 3.7**: In the code chunk below, edit the table such that the cells (including standard errors) corresponding to the variable `treat` have a red background and white text. Make sure to load the `kableExtra` library beforehand.

```{r}
library(kableExtra)
list(model1, model2, model3, model4) |>
  modelsummary(stars=T, gof_map = c("nobs", "r.squared")) |>
  row_spec(3:4, background ="red", color="white")
```

**Question 3.8**: Write a piece of code that exports this table (without the formatting) to a Word document. 

```{r}
list(model1, model2, model3, model4) |>
  modelsummary(stars=T, gof_map = c("nobs", "r.squared"),
               output = 'tableassignment4.docx')
```

## The End
